\thesistitle

### 2019-08-13 sections/background.tex

\section{Code clone terminology}\label{sec:terminology}
% The sets are actually definitions, NOT PROPERTIES. This should be clearer.
Many studies present different definitions for code clone concepts. For this study, we mainly use the definitions from Bruntink et al. \cite{bruntink2005use}, Roy et al. \cite{roy2007survey} and Jiang et al. \cite{jiang2007deckard}. We created a summary of these concepts, which can be found in table \ref{tab:clone-terminology}.

@@

\subsection{Example}
This section gives an example to make the terminology of table \ref{tab:clone-terminology} more concrete. The code fragment in figure \ref{fig:cloneclasses} shows two clone classes. One of the clone classes consists of two clone instances and has three nodes per instance. The other clone instance has three clone instances and consists of two nodes per instance.

@@

This example can be represented as a tree structure using the concepts from table \ref{tab:clone-terminology}. This tree structure is displayed in figure \ref{fig:terminologyexample}.

\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{img/TerminologyExample}
  \caption{Representation of figure \ref{fig:cloneclasses} using the terminology introduced in table \ref{tab:clone-terminology}}
  \label{fig:terminologyexample}
\end{figure}

>>>>

\section{Code clone terminology}\label{sec:terminology}
% The sets are actually definitions, NOT PROPERTIES. This should be clearer.
Many studies present different definitions for code clone concepts. For this study, we mainly use the definitions from Bruntink et al. \cite{bruntink2005use}, Roy et al. \cite{roy2007survey} and Jiang et al. \cite{jiang2007deckard}. We created a summary of these concepts, which can be found in Table~\ref{tab:clone-terminology}.

@@

\subsection{Example}
This section gives an example to make the terminology of Table~\ref{tab:clone-terminology} more concrete. The code fragment in Figure~\ref{fig:cloneclasses} shows two clone classes. One of the clone classes consists of two clone instances and has three nodes per instance. The other clone instance has three clone instances and consists of two nodes per instance.

@@

This example can be represented as a tree structure using the concepts from Table~\ref{tab:clone-terminology}. This tree structure is displayed in Figure~\ref{fig:terminologyexample}.

\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{img/TerminologyExample}
  \caption{Representation of Figure~\ref{fig:cloneclasses} using the terminology introduced in Table~\ref{tab:clone-terminology}}
  \label{fig:terminologyexample}
\end{figure}

### 2019-08-13 sections/clonerefactor.tex

\chapter{CloneRefactor} \label{ch:clonerefactor}
% We bridged a gap between clone detection and refactoring .. by designing a tool
We bridged a gap between clone detection and refactoring by designing a tool that can detect clones by our refactoring-oriented clone types (chapter \ref{chap:clonetypes}). This tool, named CloneRefactor, performs a comprehensive context analysis on the detected clones. Based on this this context, CloneRefactor can automatically refactor a subset of the detected clones by applying transformations to the source code of the analyzed software project(s).

>>>>

\chapter{CloneRefactor} \label{ch:clonerefactor}
% We bridged a gap between clone detection and refactoring .. by designing a tool
We bridged a gap between clone detection and refactoring by designing a tool that can detect clones by our refactoring-oriented clone types (chapter \ref{chap:clonetypes}). This tool, named CloneRefactor\footnote{The source code of CloneRefactor is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}, performs a comprehensive context analysis on the detected clones. Based on this this context, CloneRefactor can automatically refactor a subset of the detected clones by applying transformations to the source code of the analyzed software project(s).

### 2019-08-13 sections/discussion.tex

\chapter{Discussion}
\todo{TODO}
\label{ch:discussion}

In this chapter, we discuss the results of our experiment(s) on ...

\begin{finding}
	Highlight like this an important finding of your analysis of the results.
	\label{find:important1}
\end{finding}

Refer to Finding~\ref{find:important1}.

@@

\subsubsection{Type 2R clones}
With type 2R clones we allow variability in some identifiers and literals such that the code can and should still be refactored. For type 2R clones we chose a set of expressions in which we allow variability and proposed a recommended refactoring strategy. We think however that type 2R could still use a lot of improvement to find more duplication patterns that can be refactored.

@@

>>>>

\chapter{Discussion}
\label{ch:discussion}

In this chapter, we discuss the results of our research and experiments.

@@

\subsection{Type 2R clones}
With type 2R clones we allow variability in some identifiers and literals such that the code can and should still be refactored. For type 2R clones we chose a set of expressions in which we allow variability and proposed a recommended refactoring strategy. We think however that type 2R could still use a lot of improvement to find more duplication patterns that can be refactored.

@@

\section{CloneRefactor}
In this section we discuss our decisions for the design of our CloneRefactor tool.

\subsection{Clone Detection}
For CloneRefactor we chose to design a novel method of detecting clones, rather than using an existing clone detection technique or tool.
